Issues with Dynamical Measurements Across the Disk

### 2019-02-26 paper/ms.tex
Fix technical piece of bootstrap resampling

\subsection{Local Midplane} \label{ssec:local_midplane}
Using the three simulations, we determine the local midplane that an observer
might measure if they were situated in each of these galaxies, as a function
of azimuth at the solar circle. Starting from the coordinate system described
in the previous section, which is approximately aligned so that the $z$
coordinate is perpendicular to the disk plane, we place our imaginary observer
at $z=0$ and a solar radius of $8.2\,\kpc$ and vary the azimuth between
$0<\phi<2\pi$\footnote{Our very long-lived observer also has warp-drive.}. At
each value of $\phi$ we then compute the median $z$ for stars within a
cylinder of radius $0.5\,\kpc$ and height $1\,\kpc$ perpendicular to the
fiducial disk. We then re-define this median $z$ as the new midplane of the
cylinder, re-select stars, and iterate until the median $z$ value converges.
We find that only $10$ iterations of this procedure are necessary for
convergence. The resulting median $z$ is taken to be what our observer would
measure as the local Galactic midplane at each $\phi$. This procedure assumes
perfect density estimation, and therefore perfect corrections for extinction,
within the cylinder defining the ``solar neighborhood.'' Imperfect extinction
correction is likely to increase the amplitude of the estimated fluctuations
in $z$. To account for the effect of particle noise, we bootstrap-resample
stars within the cylinder $1000$ times and determine the $95^{\text{th}}$
minus $5^{\text{th}}$ percentile range. This bootstrap resampling is performed
by first selecting all stars within a height of $2\,\kpc$, resampling that
selection, and then repeating the $10$ iterations.

>>>>

\subsection{Local Midplane} \label{ssec:local_midplane}
Using the three simulations, we determine the local midplane that an observer
might measure if they were situated in each of these galaxies, as a function
of azimuth at the solar circle. Starting from the coordinate system described
in the previous section, which is approximately aligned so that the $z$
coordinate is perpendicular to the disk plane, we place our imaginary observer
at $z=0$ and a solar radius of $8.2\,\kpc$ and vary the azimuth between
$0<\phi<2\pi$\footnote{Our very long-lived observer also has warp-drive.}. At
each value of $\phi$ we then compute the median $z$ for stars within a
cylinder of radius $0.5\,\kpc$ and height $1\,\kpc$ perpendicular to the
fiducial disk. We then re-define this median $z$ as the new midplane of the
cylinder, re-select stars, and iterate until the median $z$ value converges.
We find that only $10$ iterations of this procedure are necessary for
convergence. The resulting median $z$ is taken to be what our observer would
measure as the local Galactic midplane at each $\phi$. This procedure assumes
perfect density estimation, and therefore perfect corrections for extinction,
within the cylinder defining the ``solar neighborhood.'' Imperfect extinction
correction is likely to increase the amplitude of the estimated fluctuations
in $z$. To account for the effect of particle noise, we bootstrap-resample
stars within a cylinder of stars with height $2\,\kpc$ and the same radius
$1000$ times and determine the $95^{\text{th}}$ minus $5^{\text{th}}$
percentile range. This bootstrap resampling is performed by first selecting
all stars within a height of $2\,\kpc$, resampling that selection, and then
repeating the $10$ iterations.
